---
title: "Atomic Vector"
author: "kittipos sirivongrungson"
date: '2022-05-23'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Create Atomic Vector

You can create atomic vector with `c()` function.

```{r}
?c
```

Atomic vector must have elements with the **same** type (Note that `NA` denotes missing value)

### Character Vector

```{r}
# Character Vector
c("Harry", "Ron", "Hermione", NA)
```

### Numeric Vector

```{r}
## Double Vector
c(1, 2.2, NA)
## Integer vector
c(1L, 2L, 3L, 4L, 5L)
```

A shorthand version is:

```{r}
1:5
-2:2
```


### Logical Vector

```{r}
c(T, F, NA)
```



## Coercion

What if we combine different types

```{r}
(combined <- c(FALSE, 1, "Harry"))
```

The result will be **coerced** in this order: 

> logical -> integer -> double -> character
    

```{r}
typeof(combined)
```

## Length of Vector

```{r}
?length
```

```{r}
students <- c("Harry", "Ron", "Hermione", NA)

length(students)
length("Hello") # length of a scalar
```

## Subset Vector

Subset vector by using square brackets: `[` or `[[` (preferred)

```{r}
(students <- c("Harry", "Ron", "Hermione"))
```

The **first student** is:

```{r}
students[1]
students[[1]]
```

The **last student** is:

```{r}

```

or another way using `length()`

```{r}

```




