---
title: "More on Vector"
author: "kittipos sirivongrungson"
date: '2022-05-23'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Length of Vector

```{r}
students <- c("Harry", "Ron", "Hermione", NA)
```

## Subset Vector

Subset vector by using square brackets: `[` or `[[` (preferred)


### Integer subsetting

```{r}
(students <- c("Harry", "Ron", "Hermione"))
```

The **first student** is:

```{r}

```

The **last student** is:


```{r}


```

or another way using `length()`

```{r}

```

**Subset multiple values**

```{r}

```

Negate selection with negative number.

```{r}

```





### Logical subsetting

```{r}
(students <- c(rep("Harry", 3), "Ron", "Hermione", "Harry"))
```


Subset "Harry"

```{r}


```

Subset "Harry" and "Ron"

```{r}


```

## Named Vector 

### Create (Option 1)

Create named vector by `c(name_1 = value_1, name_2 = value_2, ...)`,

where name must be a character, and value can be any atomic type.

```{r}
score <- c(Harry = 8, Ron = 7, Hermione = 10)
score
```

Get names of vector by `names()`

```{r}
?names
score_nm <- names(score)
score_nm
```


### Create (Option 2)

Create named vector from 2 vectors:

```{r}
score <- c(8, 7, 10)
students <- c("Harry", "Ron", "Hermione")


```

### Subset Named Vector

Subset by **position**

```{r}


```

Subset by **name**


```{r}


```


