---
title: "Atomic Vector"
author: "kittipos sirivongrungson"
date: '2022-05-23'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Create Atomic Vector

You can create atomic vector with `c()` function.

```{r}
?c
```

Atomic vector must have elements with the **same** type (Note that `NA` denotes missing value)

### Character Vector

```{r}
# Character Vector
c("Harry", "Ron", "Hermione", NA)
```

### Numeric Vector

```{r}
## Double Vector
c(1, 2.2, NA)
## Integer vector
c(1L, 2L, 3L, 4L, 5L)
```

A shorthand version is:

```{r}
1:5
-2:2
```


### Logical Vector

```{r}
c(T, F, NA)
```



## Coercion

What if we combine different types

```{r}
(combined <- c(FALSE, 1, "Harry"))
```

The result will be **coerced** in this order: 

> logical -> integer -> double -> character
    

```{r}
typeof(combined)
```

## Operators with Vector

### Math Operators

Most math operations are **element-wise** operations on vectors:

```{r}
(x <- 1:5)

x + 10
x * 10
x / 10

2 ^ x

x %% 2
```

Some are not element-wise, such as Matrix multiplication:

```{r}
x %*% x # Inner Product 
x %o% x # Outer Product
```

### Logical Operators

Logical operations are **element-wise** operations on vector:

```{r}
(x <- 1:5)

x == 2
x != 2

x >= 2
```


## Length of Vector

```{r}
?length
```

```{r}
students <- c("Harry", "Ron", "Hermione", NA)

length(students)
length("Hello") # length of a scalar
```

## Subset Vector

Subset vector by using square brackets: `[` or `[[` (preferred)

### Logical subsetting

```{r}
(students <- c("Harry", "Ron", "Hermione"))
```

```{r}
students[c(TRUE, FALSE, FALSE)]

students == "Harry"

students[students == "Harry"]
```


### Integer subsetting

```{r}
(students <- c("Harry", "Ron", "Hermione"))
```

The **first student** is:

```{r}
students[1]
students[[1]]
```

The **last student** is:


```{r}


```

or another way using `length()`

```{r}

```

**Subset multiple values**

```{r}
students[c(1,2)]
students[1:2]
```

Negate selection with negative number.

```{r}
students[-1]
```




## Named Vector 

### Create (Option 1)

Create named vector by `c(name_1 = value_1, name_2 = value_2, ...)`,

where name must be a character, and value can be any atomic type.

```{r}
score <- c(Harry = 8, Ron = 7, Hermione = 10)
score
```

```{r}
typeof(score)
```

Get names of vector by `names()`

```{r}
?names
score_nm <- names(score)
score_nm
```

```{r}
typeof(score_nm) # Names is a character vector
```

### Create (Option 2)

Create named vector from 2 vectors:

```{r}
score <- c(8, 7, 10)
students <- c("Harry", "Ron", "Hermione")

names(score) <- students
score
```

### Subset Named Vector

Subset by **position**

```{r}
score[1] 
score[[1]] # No names
```

Subset by **name**

```{r}
score["Harry"]
score[["Harry"]] # No names
```


