---
title: "Control Flow"
author: "kittipos sirivongrungson"
date: '2022-05-26'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loop

`for` loop is popular in R

## Loop for Side Effect

Loop Over Vector

```{r}
friends <- c("Amy", "Tom", "Jelly")



```

Loop Over Index (usually use more often)

using `seq_along()` is recommended

```{r}
friends <- c("Amy", "Tom", "Jelly")


```


## Loop for Assign Value (Common)

Step 1: Create empty vector to store output. You can use `vector()` function

Step 2: Loop over desired vector and assign each elements to each element of output.

Example

```{r}
friends <- c("Amy", "Tom", "Jelly")
```


```{r}
# Create Empty Vector


# Loop over elements and assign value of each elements to output vector


```

This is actually redundant because `paste` is already a vectorized function.

```{r}

```





# Conditionals

## Syntax

### `if` statement

The syntax is:

```{r eval=FALSE}
if (condition_1) {
  
  option_1
  
} else if (condition_2) {
  
  option_2
  
} else {
  
  catch_all

}
```


### `ifelse()`

```{r eval=FALSE}
ifelse(condition, code_if_true, code_if_false)
```




### Compare Number: Version 1

```{r}
x <- 2
y <- 5

if(x < y) cat("x is less than y")

if(x > y) cat("x is greater than y")

if(x == y) cat("x is equal to y")
```

```{r}
compare <- function(x, y) {
  

  
}
```

```{r}
compare(x = 1, y = 2)
compare(x = 2, y = 1)
compare(x = 1, y = 1)
```


### Compare Number: Version 2


```{r}
compare <- function(x, y) {
  

}
```

```{r}
compare(x = 1, y = 2)
compare(x = 2, y = 1)
compare(x = 1, y = 1)
```

### Parity

Testing even vs odd number

```{r}
parity <- function(x){
  

}
```


```{r}
parity(0)
parity(1)
parity(2)
```

### Parity (Vectorized)

How to test parity every elements in a vector

```{r}
nums <- c(1:3, 8:10)
```

#### Loop

```{r}
out <- vector("numeric", length(nums))

for (i in seq_along(nums)) {
  
  out[i] <- parity(nums[i])
  
}

out
```

Shorter looping with `sapply()`

```{r}
sapply(nums, parity)
```

#### Ifelse

Vectorized Version with `ifelse()` 

```{r}
parity_vec <- function(x) {
  

  
}
```

```{r}
parity_vec(nums)
```

#### Logical Subsetting

Logical Subsetting (the fastest way)

```{r}
parity_subset <- function(x) {
  

  
}

parity_subset(nums)
```


### Homework: Grade

Create grading function `grade()`

If score in range

[90, 100]: "A"

[80, 90): "B"

[70, 80): "C"

[60, 70): "D"

Otherwise: "F"

```{r}
grade <- function(score) {
  

}
```



